---
title: "Multi-chunk programs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Multi-chunk programs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, register the `dotnet` knitr engine:

```{r setup}
dotnet::register_engine()
```

For single-chunk programs, new .NET app is created either in a temporary directory or in the chunk's cache (if `cache` chunk option is set to `TRUE`). For multi-chunk programs, we will need to manage the app directory ourselves and keep it consistent between the chunks.

```{r app_settings}
app_name <- "multiChunkProgram"
app_dir <- file.path(tempdir(), app_name)
```

Also, until the app is ready to be run we will need to specify `run_app = FALSE` in each chunk's `engine.opts`:

````{verbatim}
```{dotnet MyClass, engine.opts = list(file = 'MyClass', name = app_name, dir = app_dir, run_app = FALSE)}
class MyClass {
}
```
````

Once we're ready to define the `Main()` method, we conclude with:

````{verbatim}
```{dotnet Program, engine.opts = list(name = app_name, dir = app_dir)}
class Program {
  static void Main(string[] args) {
    // Code to be executed
  }
}
```
````

Notice the missing `file` and `run_app` in `engine.opts`. That's because `file` is "Program" and `run_app = TRUE` by default, since single-chunk programs are the default.

## Example

```{dotnet author, engine.opts = list(file = 'Author', name = app_name, dir = app_dir, run_app = FALSE)}
class Author {
  public string name;
  public int dob; // date of birth
  public int dod; // date of death
  public Author(string name, int dob, int dod) {
    this.name = name;
    this.dob = dob;
    this.dod = dod;
  }
  public int age { get { return dod - dob; } }
}
```

```{dotnet book, engine.opts = list(file = 'Book', name = app_name, dir = app_dir, run_app = FALSE)}
class Book {
  public string title;
  public int year;
  public Author author;
  public Book(string title, int year, Author author) {
    this.title = title;
    this.year = year;
    this.author = author;
  }
}
```

```{dotnet program, engine.opts = list(file = 'Program', name = app_name, dir = app_dir, run_app = TRUE)}
using System;

class Program
{
  static void Main(string[] args)
  {
    Author kv = new Author("Kurt Vonnegut Jr.", 1922, 2007);
    Book cc = new Book("Cat's Cradle", 1963, kv);
    Console.WriteLine("'{0}' ({1}) by {2}", cc.title, cc.year, cc.author.name);
    Console.WriteLine("{0} was {1} or so when he died in {2}", kv.name, kv.age, kv.dob);
  }
}
```
